---
title: "coding_exercise"
author: "Samantha Nauman"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
source("setup.R")
```

Load Data
```{r}
data("knz_bison")
```

1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
knz_bison <- knz_bison %>%
  mutate(age_years = rec_year - animal_yob)
```

2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
filter_bison_by_weight <- function(weight_threshold) {
  knz_bison %>%
    filter(animal_weight >= weight_threshold)
}
```

3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
# Boxplot
ggplot(knz_bison, aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(
    title = "Weight Distribution of Bison by Sex",
    x = "Sex",
    y = "Weight (kg)"
  ) +
  theme_bw()

# T-test
t_test(animal_weight ~ animal_sex, data = knz_bison, var.equal = FALSE, detailed = TRUE) %>%
  View()
```

- Statistically significant difference in weight between male and female bison. 
